Output Summary

### 2023-05-04 03-post-process/output-plots-children/06-length-based-survival.Rmd
Consistency updates: 06-length-based-survival.Rmd

## Parr $\to$ Smolt Overwinter Survival

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j, i) {

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
       xlim = range(L_Pb_seq), 
       main = ifelse(i == 1, pops[j], "")
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

plot_fn2 = function(j) {
    # create the plots for both migratory strategies
  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
}

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn2)
mtext(side = 1, line = 1.5, outer = T, "Parr Mean Length (mm)", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

## Smolt Survival to LGR

```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
plot_fn = function(j) {

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
       xlim = range(L_Mb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Smolt Mean Length (mm)")
mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
```

>>>>

## Parr $\to$ Smolt Overwinter Survival {.tabset .tabset-pills}

```{r phi_Pa_Mb_lim}
phi_Pa_Mb_lim = make_lim_param(post, "^phi_Pa_Mb[")
```

### Time Series {.tabset .tabset-pills}

#### Fall Migrants {.tabset .tabset-pills}

##### Realized Alone

```{r phi_Pa_Mb_tseries-fall-1, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Overwinter Survival (Fall Migrants)")
```

##### Realized + Predicted

```{r phi_Pa_Mb_tseries-fall-2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )

  # predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
              yrs = all_yrs[t])

}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Overwinter Survival (Fall Migrants)")
```

#### Spring Migrants {.tabset .tabset-pills}

##### Realized Alone

```{r phi_Pa_Mb_tseries-spring-1, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Overwinter Survival (Spring Migrants)")
```

##### Realized + Predicted

```{r phi_Pa_Mb_tseries-spring-2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )

  # predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)),
              yrs = all_yrs[ts_yrs])

}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Overwinter Survival (Spring Migrants)")
```

### Mean Length Relationship {.tabset .tabset-pills}

```{r}
plot_f = function(j, i) {

@@

  plot(1,1, type = "n", 
       ylim = phi_Pa_Mb_lim,
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = tran_cols["model"])
  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = main_cols["model"], lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = main_cols["model"])
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = main_cols["model"])
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
  box(col = par("col.axis"))
}
```

#### Fall Migrants

```{r phi_Pa_Mb_fall_relationship, fig.width = p4_width, fig.height = p4_height}
mypar()
junk = sapply(1:jags_data$nj, plot_f, i = 1)
axis_labels("Parr Mean Length (mm)", "Overwinter Survival (Fall Migrants)")
```

#### Spring Migrants

```{r phi_Pa_Mb_spring_relationship, fig.width = p4_width, fig.height = p4_height}
mypar()
junk = sapply(1:jags_data$nj, plot_f, i = 2)
axis_labels("Parr Mean Length (mm)", "Overwinter Survival (Spring Migrants)")
```

## Smolt $\to$ LGR Survival {.tabset .tabset-pills}

```{r phi_Mb_Ma_lim}
phi_Mb_Ma_lim = sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = ".", LH_type = i_spring, origin = o_nor) |>
  make_lim_param(post, param = _)
```

### Time Series {.tabset .tabset-pills}

#### Realized Alone

```{r phi_Mb_Ma_tseries-1, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
  )
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR)")
```

#### Realized + Predicted

```{r phi_Mb_Ma_tseries-2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
  )

  # predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Mb_Ma_dot[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)),
              yrs = all_yrs[ts_yrs])

}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR)")
```

### Mean Length Relationship

```{r toLGR-survival-plots, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
       ylim = phi_Mb_Ma_lim,
       xlim = range(L_Mb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tran_cols["model"])
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = tran_cols["model"], lwd = 2)

  # realized pairs
  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = main_cols["model"])
  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = main_cols["model"])
  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
  text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
  box(col = par("col.axis"))
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Smolt Mean Length (mm)", "Smolt \u2192 LGR Survival (NOR)")
```
